### 2020-06-01 writeup/experiments.tex
sec 5
sec 5 tl

\textbf{Improving multi-task training efficiency.}
We compare Algorithm \ref{alg_inc_train} to performing multi-task learning.
Over six randomly selected task pairs from the sentiment analysis tasks, we find that Algorithm \ref{alg_inc_train} requires only $45\%$ of the computational cost to achieve the same performance on the target task, compared to the multi-task learning baseline.

\textbf{Improving transfer learning training efficiency.}
\todo{}

>>>>

\textbf{Improving multi-task training efficiency.}
We compare Algorithm \ref{alg_inc_train} to performing multi-task learning for predicting a particular target dataset.
Over six randomly selected task pairs from the sentiment analysis tasks, we find that Algorithm \ref{alg_inc_train} requires only $45\%$ of the computational cost to achieve the same performance on the target task, compared to the multi-task learning baseline.

\textbf{Improving transfer learning training efficiency.}
We show that Algorithm \ref{alg_inc_train} also applies to transfer learning settings.
Compared to fine-tuning the source model on the target task, we show that our proposed method reduces the computional cost by \alert{$xx\%$}, without sacrificing accuracy.
